NumPy---Array Programming in Python

### 2020-01-31 body.tex
Update captions

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array-concepts}   
  \caption{\textbf{Fundamental Array Concepts.}
    \textbf{a,} The NumPy array data structure and its associated metadata fields.
    \textbf{b,} Indexing an array with various types of arguments.
    \textbf{c,} Indexing with arrays, which broadcast the indexing arguments before performing the lookup.
    \textbf{d,} Vectorization efficiently applies operations to groups of elements
    \textbf{e,} Broadcasting in scalar addition, and in the division of two-dimensional arrays.
    \textbf{e,} Reduction operations act along one or more axes. In this
    example, a three-dimensional array is shown to be summed along various single
    axes to produce two-dimensional results, or along two axes consecutively to
    produce a one-dimensional result.
   }
  \label{fig:array-concepts}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=.9\textwidth]{static/sketches/array_protocol.jpg}
  \caption{\textbf{Interoperability.} \fixme{This figure needs work.}}\label{fig:duck-arrays}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array-concepts}   
  \caption{\textbf{Fundamental Array Concepts.}
    \textbf{a,} The NumPy array data structure and its associated metadata fields.
    \textbf{b,} Indexing an array with various types of arguments.
    \textbf{c,} Indexing with arrays, which broadcast the indexing arguments before performing the lookup.
    \textbf{d,} Vectorization efficiently applies operations to groups of elements
    \textbf{e,} Broadcasting in scalar addition, and in the division of two-dimensional arrays.
    \textbf{f,} Reduction operations act along one or more axes. In this
    example, a three-dimensional array is shown to be summed along various single
    axes to produce two-dimensional results, or along two axes consecutively to
    produce a one-dimensional result.
    \textbf{g,} Example NumPy code, illustrating some of these concepts.
   }
  \label{fig:array-concepts}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=.9\textwidth]{static/sketches/array_protocol.jpg}
  \caption{\textbf{Interoperability.} Through its array protocol, the NumPy API can operate on various types of array objects, including those written outside of NumPy. In this example, NumPy's \code{sum} function is called on a NumPy and a dask array, respectively. The call gets succeeds by dispatching to the appropriate library implementation, and results in different output array types.}\label{fig:duck-arrays}
\end{figure*}
